### 2019-02-11 tex_v2/manuscript.tex
edits and begin conclusions

	While this behavior has been observed in many species of \textit{Curculio}, it was unclear how the rostrum of female acorn weevils can withstand the repeated, often extreme bending incurred during the process of egg-chamber excavation.
	In this study we characterize the composite profile of the rostral cuticle to account for the observed flexibility of the snout.
	We show that the relative layer thicknesses and fiber orientation angles of the exocuticle and endocuticle of the rostrum are strongly differentiated from the head capsule and other body parts, and we estimate the effect of these differences using Classical Laminate Plate Theory (CLPT).

	Because recent studies have shown that the yield strength of the weevil rostrum exoskeleton is lower in tension than compression, we perform a comparative analysis of the ultimate tensile strength of the rostrum across species and snout morphotypes; we also report the results of displacement-controlled load cycling of the snout in a species with strongly curved morphology.
	We relate an observed increase in the volume fraction of endocuticle in the rostrum to higher tensile strength at the rostral apex in all tested species, and find that a strongly curved rostrum can be flexed repeatedly without harm to the structure.

	We additionally describe the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	Based on our findings, we posit that the composite profile of the rostral apex enables the snout to be flexed until straight while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton.
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
	\info{780 words, reduce in revisions}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin fibers; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other, thus forming a quasi-isotropic laminate referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This layout effectively produces a transversely isotropic composite, mitigating the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton.

@@

		Serial thin sectioning and scanning electron microscopy of fractured \textit{Curculio} specimens has revealed that endocuticle in the head capsule fits this general profile, with an angle of approximately $30\degree$ between successive pairs of pseudo-orthogonal plies.
		Additionally, in the head capsule, the thickness of the exocuticle in cross section is nearly equal to that of the endocuticle\info{thickness measurements here}.
		However, we have also found that the cuticle composite lay-up of the rostral apex differs from that of the head capsule (see Fig.\info{~INSERT-REFS-HER}) in two key characteristics:

		\begin{enumerate}
			\item The exocuticle is reduced to a thin shell\info{measurement here}, with the endocuticle thickened \info{measurement here} to offset this reduction to maintain a constant cuticle thickness in the head.
			\item The endocuticular macrofibers exhibit no rotation between successive pseudo-orthogonal plies, which are all oriented at approximately $\pm45\degree$ to the longitudinal axis of the snout (i.e., an antisymmetric $[\pm45\degree]$ angle-ply laminate).
		\end{enumerate}

@@

		To assess the individual contributions of layer thickness and stacking angle sequence to cuticle flexibility in the rostral apex, two hybrid cuticle lay-ups were also modeled, each with only one of the modifications, namely:
		\begin{enumerate}
			\item A hybrid cuticle with the angle stacking sequence of regular cuticle (the head capsule) but possessing the layer thicknesses of the rostral apex. $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases, respectively.
			\item A hybrid cuticle with the layer thicknesses of regular cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle). $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases, respectively.
		\end{enumerate}

@@

	\section{Force-controlled loading to fracture}
	%600 words... still must add numbers...

		To better characterize the mechanical behavior of the rostrum at failure, we performed tensile testing on the snouts of six \textit{Curculio} species, representing a mixture of closely and distantly related taxa.
		Heads of female specimens of each species were rehydrated by immersion in de-ionized water for 24 hours
		Each specimen was subjected to force-controlled, uniaxial loading to fracture at a constant stress rate (detailed in Methods).
		We then examined the correspondence between composite structure and mechanical behavior of the snout, using phylogenetic linear mixed effects models to account for phylogenetic non-independence in the residual variances of the models.

		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in apparently brittle fracture after a period of strain hardening.
		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Consequently, there was a negative correlation between ultimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		Inversely, the failure strength of the cuticle is positively associated with the relative proportion of the endocuticle.

		Although CLPT predicts that the proportion of exocuticle is positively correlated with the stiffness of generalized cuticle, we found no associations between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.
		Instead, we found that the uniaxial elastic modulus of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec)
		These associations were all found to be statistically significant and independent of species membership.

		Additionally, we observed a moderate stiffening size-effect with respect to rostral length.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) snout would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this may be the result of a longer transition gradient from the basal profile to the apical profile in longer rostra.
		We hypothesize that a decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.

		From these results, we infer that the gross elastic behavior of the cuticle is consistent across the genus, in agreement with our current understanding of cuticle mechanobiology.
		It is therefore unlikely that differences in sclerotization or chitin composition within the cuticle, rather than composite profile, are responsible for the mechanical behavior of the rostrum in different species.
		Furthermore, the endocuticle apparently contributes more to the tensile strength of the rostrum than the exocuticle, likely because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Thus, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

@@

	\section{Fractography of test specimens}
	%currently ~650 words
		Due to the complex failure patterns present across the fracture surface, it was not always possible to identify void nucleation and crack initiation sites (both primary and secondary).
		Nonetheless, we observed several patterns characteristic of both the micro-scale behavior of the cuticle and the meso-scale behavior of the rostrum during uniaxial tensile failure, which we describe here.

		Scanning electron and light microscopy of testing specimens revealed that the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure.	
		In transverse view, the exocuticle consistently presented a nearly continuous fracture surface, indicative of comparatively brittle failure, likely due to the helicoidal arrangement of \textalpha-chitin laminae and resultant transverse isotropy of the Bouligand structure.
		The exocuticle typically appeared to fracture at lower strains than the endocuticle, with shear-cusp formation evident across the fracture surface and over unbroken endocuticle on the rostral surface adjacent to the plane of fracture.
		Conversely, the endocuticle exhibited severe delamination, off-axis ply-splitting, and fiber-pulling away from the fracture surface, indicating that endocuticular macrofibers are less brittle than the exocuticle due to the unidirectional alignment of their \textalpha-chitin fibers.
		Because the exocuticle of weevils is anchored to the endocuticle by cross-linking fibers, the presence of exocuticular shear-cusp formation in uniaxial tension suggests extension-shear coupling within individual endocuticle laminae, which caused ply-splitting via mode II fracture between macrofibers at high strain.
		This intra-laminar extension-shear coupling also yielded off-axis in-plane resultant forces as a function of lamina orientation angle; mode III shearing then occurred between laminae with opposing in-plane resultant forces, causing inter-ply delamination.
		Tensile failure of the macrofiber laminae would ultimately occur via mixed-mode I/II (transverse tension/intra-laminar shear) fracture due to an increase in applied stress caused by ply-splitting in adjacent laminae.

		At the meso-scale, most specimens fractured along a single plane across and between the occipital sulci, which are cuticle invaginations that traverse the entire length of the rostrum.
		These sulci increase the volume fraction of exocuticle in the ventral part of the snout and create large interfaces ideal for void nucleation.
		The exocuticle of the occipital sulci usually displayed shear cusps oriented outward from the center of the invagination, continuing dorsolaterally and ventromedially.
		Ventrally the cusps converged toward a prominent scarp where the crack fronts joined, although in specimens with large cross-sectional areas of endocuticle, this was often obscured by delaminated endocuticular macrofibers.

		The first layer of endocuticle usually fractured along the same plane as the exocuticle, and ventrally the endocuticle laminae typically converged toward a scarp-like region characterized by severe delamination and numerous de-bonded macrofibers.
		Additionally, macrofibers oriented in the direction of crack propagation exhibited extensive ply-splitting with intermittent transverse shearing, while macrofibers oriented against the direction of crack propagation primarily displayed fracture by transverse shear along the plane of ply-splitting in adjacent laminae.
		Thus, contralateral fibers in the same lamina displayed opposing fracture modes.
		In addition, the ventrolateral surfaces often exhibited extensive inter-ply delamination and fiber de-bonding in scarp-like prominences, likely due to a combination of tensile failure and shearing along the dorsally-radiating crack front.
		Dorsally, the coalescent crack fronts often caused significant de-bonding and ply-splitting followed by broom-like tensile failure; in some specimens, the contralateral crack fronts were out of plane and coalesced via transverse shearing through a large dorsal section of cuticle.

		From these patterns we hypothesize that the exocuticle-rich occipital sulci are the most likely site for the initiation of void nucleation and catastrophic failure of the integrated rostral cuticle in cross section, as illustrated in Fig~REF.
		According to this model, structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
		Although other, more complex failure modes have been observed, we posit that in live specimens this is the most likely mechanism of tensile failure because typical bending behavior generates tension along the ventral surface of the rostrum.

	\section{Conclusions}
	%1-2 'short paragraphs', 300 words maximum, already at 3200...
		In this study, we...
		raising the intriguing possibility that this system evolved via negative selection of breakage, rather than positive selection of flexibility.\info{(maybe say this in conclusions)}

		evolutionary constraint (like occipital sulci)

		The macrofibers are pulled longitudinal axis, explains fmax, toughness, and upcurved stress-strain curve.

		We therefore infer that, under uniaxial tension, the endocuticle deforms viscoelastically along the longitudinal axes of the macrofibers, causing ply-splitting and delamination at high strain, while the overlying exocuticle exhibits brittle fracture, at a comparatively low strain, due to shearing between the stretching endocuticle fibers to which it is anchored.
		This outcome is consistent with behavior shown in previous studies and is congruent with theoretical consideration of cuticle microstructure in CLPT, which predicts extension shear-coupling ($A_{16}, A_{26}\neq{0}$) for individual off-axis macrofiber laminae.

>>>>

	While this behavior has been observed in many species of \textit{Curculio}, it was unclear how the rostrum of female acorn weevils can withstand the repeated, often extreme bending incurred during the process of egg-chamber excavation.
	In this study we characterize the composite profile of the rostral cuticle to account for the observed flexibility of the snout.
	We show that the relative layer thicknesses and fiber orientation angles of the exocuticle and endocuticle of the rostrum are strongly differentiated from the head capsule and other body parts, and we estimate the effect of these differences on the elasticity of the cuticle using Classical Laminate Plate Theory (CLPT).

	Because recent studies have shown that the yield strength of the beetle exoskeleton is lower in tension than compression, we perform a comparative analysis of the ultimate tensile strength of the rostrum across species and snout morphotypes; we also report the results of displacement-controlled load cycling of the snout in a species with strongly curved morphology.
	We relate an observed increase in the volume fraction of endocuticle in the rostrum to higher tensile strength at the rostral apex in all tested species, and find that a strongly curved rostrum can be flexed repeatedly without harm to the structure.

	We additionally describe the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	Based on our findings, we posit that the composite profile of the rostral apex enables the snout to be flexed until straight while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton.
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
	\info{780 words, reduce in revisions}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin nanofibrils; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other, thus forming a quasi-isotropic laminate referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This layout effectively produces a transversely isotropic composite, mitigating the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton.

@@

		Serial thin sectioning and scanning electron microscopy of fractured \textit{Curculio} specimens have revealed that endocuticle in the head capsule fits this general profile, with an angle of approximately $30\degree$ between successive pairs of pseudo-orthogonal plies.
		Additionally, in the head capsule, the thickness of the exocuticle in cross section is nearly equal to that of the endocuticle\info{thickness measurements here}.
		However, we have also found that the cuticle composite lay-up of the rostral apex differs from that of the head capsule (see Fig.\info{~INSERT-REFS-HER}).
		Distally the exocuticle is reduced to a thin shell\info{measurement here}, with the endocuticle thickened \info{measurement here} to offset this reduction and maintain a constant cuticle thickness in the head.
		Moreover, the endocuticular macrofibers exhibit no rotation between successive pseudo-orthogonal plies, which are all oriented at approximately $\pm45\degree$ to the longitudinal axis of the snout (i.e., an antisymmetric $[\pm45\degree]$ angle-ply laminate).

@@

		To assess the individual contributions of layer thickness and stacking angle sequence to cuticle flexibility in the rostral apex, two hybrid cuticle lay-ups were also modeled, each with only one of the modifications.
		A hybrid configuration with the angle stacking sequence of typical cuticle (i.e., in the head capsule) but possessing the layer thicknesses of the rostral apex had effective moduli $E_m~=~3.73\,\text{GPa}, E_f~=~4.31\,\text{GPa}$, representing 22\% and 29\% decreases from unmodified cuticle, respectively.
		Similarly, a hypothetical cuticle with the layer thicknesses of ordinary cuticle but possessing the angle stacking sequence of the rostral apex (i.e., $\pm45\degree$ angle-ply in the endocuticle) exhibited elastic moduli $E_m~=~3.77\,\text{GPa}, E_f~=~5.76\,\text{GPa}$, representing 21\% and 4.7\% decreases from unmodified cuticle, respectively.

@@

	\section{Force-controlled loading to fracture}
	%590 words... still must add numbers...

		To better characterize the mechanical behavior of the rostrum at failure, we performed tensile testing on the snouts of six \textit{Curculio} species, representing a mixture of closely and distantly related taxa.
		Heads of female specimens of each species were rehydrated by immersion in de-ionized water for 24 hours to simulate the condition of the living tissue (but see Klocke and Schmitz 2009).
		Each specimen was subjected to force-controlled, uniaxial loading to fracture at a constant stress rate of $0.05\,\text{N}\cdot\text{s}^{-1}$ (detailed in Methods).
		We then examined the correspondence between composite structure and mechanical behavior of the snout, using phylogenetic linear mixed effects models to account for phylogenetic non-independence in the residual variances of the models.

		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in apparently brittle fracture after a period of strain hardening.
		We believe that strain hardening prior to fracture is a consequence of stiff longitudinal axis of the macrofibers becoming more closely aligned to the longitudinal axis of the rostrum, thereby resisting tension more directly at higher strains.
		We observed that the maximum force sustained at the site of failure was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Consequently, there was a positive correlation between ultimate tensile strength of the specimen and the ratio of endocuticle to exocuticle cross-sectional area at the site of fracture.

		Although CLPT predicts a positive association between the proportion of exocuticle and stiffness of a generalized cuticle, we found no correspondence between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.
		Instead, we found that the uniaxial elastic modulus of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec)
		These associations were all found to be statistically significant and independent of species membership.

		Additionally, we observed a moderate, stiffening size-effect with respect to rostral length.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) snout would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this may be the result of a longer transition gradient from the basal profile to the apical profile in longer rostra.
		We hypothesize that a decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.

		From these tests, we infer that the gross elastic behavior of the cuticle is consistent across the genus, in agreement with our current understanding of cuticle mechanobiology.
		It is therefore unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum in different species; instead, a single mechanism (i.e. the modified composite profile) confers increased flexibility and tensile strength to the rostral apex in the genus \textit{Curculio}.
		he endocuticle demonstrably contributes more to rostral tensile strength than the exocuticle, likely because of its organization into large bundles of aligned, anisotropic fibers.
		Consequently, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

@@

	\section{Fractography of test specimens}
	%currently ~650 words
		Following tensile testing, the fractured specimens were subjected to fractographic analysis using light and scanning electron microscopy.
		Due to the complex failure modes evident upon examination of the fractured specimens, it was not always possible to identify void nucleation and crack initiation sites (both primary and secondary).
		Nonetheless, we observed several patterns characteristic of both the micro-scale behavior of the cuticle and the meso-scale behavior of the rostrum during uniaxial tensile failure, which we describe here.

		In transverse view, the exocuticle consistently presented a nearly continuous fracture surface, indicative of comparatively brittle failure, due to the helicoidal arrangement of \textalpha-chitin laminae and resultant transverse isotropy of the Bouligand structure (REF).
		The exocuticle typically appeared to fracture at lower strains than the endocuticle, with shear-cusp formation evident both at the fracture surface and across unbroken endocuticle on the rostral surface adjacent to the plane of fracture.
		Conversely, the endocuticle exhibited severe delamination, off-axis ply-splitting, and fiber-pulling away from the fracture surface, indicating that endocuticular macrofibers are less brittle than the exocuticle, likely as a consequence of the unidirectional alignment of their \textalpha-chitin nanofibrils (REF).
		Because the exocuticle of weevils is anchored to the endocuticle by cross-linking fibers, the presence of exocuticular shear-cusp formation in uniaxial tension suggests extension-shear coupling within individual endocuticle laminae, which caused ply-splitting via mode II fracture between macrofibers at high strain.
		This intra-laminar extension-shear coupling also yielded off-axis, in-plane resultant forces as a function of lamina orientation angle; mode III shearing then occurred between laminae with opposing in-plane resultant forces, causing inter-ply delamination.
		Tensile failure of the macrofiber laminae would ultimately occur via mixed-mode I/II (transverse tension/intra-laminar shear) fracture due to an increase in applied stress caused by ply-splitting in adjacent laminae.

		At the meso-scale, most specimens fractured along a single plane across and between the occipital sulci, which are cuticle invaginations that traverse the entire length of the rostrum.
		These sulci increase the volume fraction of exocuticle in the ventral part of the snout and contain large interfaces ideal for void nucleation.
		The exocuticle of the occipital sulci usually displayed shear cusps oriented outward from the center of the invagination, continuing dorsolaterally and ventromedially.
		Ventrally the cusps converged toward a prominent scarp where the crack fronts joined, although in specimens with large cross-sectional areas of endocuticle, this was often obscured by delaminated endocuticular macrofibers.

		The first layer of endocuticle usually fractured along the same plane as the exocuticle, and ventrally the endocuticle laminae typically converged toward a scarp-like region characterized by severe delamination and numerous de-bonded macrofibers.
		Additionally, macrofibers oriented in the direction of crack propagation exhibited extensive ply-splitting with intermittent transverse shearing, while macrofibers oriented against the direction of crack propagation primarily displayed fracture by transverse shear along the plane of ply-splitting in adjacent laminae.
		Because the laminae form a cylinder, contralateral fibers in the same lamina display opposing fracture modes.
		In addition, the ventrolateral surfaces often exhibited extensive inter-ply delamination and fiber de-bonding in scarp-like prominences, likely due to a combination of tensile failure and shearing along the dorsally-radiating crack front.
		Dorsally, the coalescent crack fronts often caused significant de-bonding and ply-splitting followed by broom-like tensile failure; in some specimens, the contralateral crack fronts were out of plane and coalesced via transverse shear through a large dorsal section of cuticle.

		From these patterns we hypothesize that the exocuticle-rich occipital sulci are the most likely site for the initiation of void nucleation and catastrophic failure of the integrated rostral cuticle in cross section, as illustrated in Fig~REF.
		According to this model, structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
		Although other, more complex failure modes have been observed, we posit that in live specimens this is the most likely mechanism of tensile failure because typical bending behavior generates tension only along the ventral surface of the rostrum.

	\section{Conclusions}
	%word count: (3157 so far...)
	%Par 1 - Microstructure
	%Par 2 - Tensile and fatigue
	%Par 3 - Fracture
	%Par 4 - Wrap-up
		The rostrum of \textit{Curculio} is characterized by a discontinuous composite profile, wherein the cuticle is strongly differentiated along an anterior-posterior gradient.
		In particular, the cuticle in the apical portion of the rostrum exhibits marked reduction in relative thickness of the and in stacking-angle between pseudo-orthogonal plies of the endocuticle, which are aligned at $\pm45\degree$ to the longitudinal axis of the snout.
		Constitutive models demonstrated that an idealized apical cuticle could theoretically achieve 72\% and 60\% reductions in the effective longitudinal membrane and flexural moduli, respectively, compared to the cuticle of the head capsule, thus accounting for the observed flexibility of the rostral apex in live specimens. However, these reductions could only be realized with both modifications to the cuticle, which have a non-additive effect on cuticle elasticity.
		Tensile testing data revealed that increased endocuticle thickness enhances the fracture toughness of the cuticle, raising the intriguing possibility that this system evolved via negative selection of breakage, rather than positive selection of flexibility.

		We confirmed that altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant, and .

		Based on fractographic analysis of test-specimens, we infer that the endocuticle deforms viscoelastically along the longitudinal axes of the macrofibers under uniaxial tension, causing ply-splitting and delamination at high strain.
		The overlying exocuticle then exhibits brittle fracture, at a comparatively low strain, due to shearing between the stretching endocuticle fibers to which it is anchored.
		This outcome is consistent with behavior shown in previous studies and is congruent with theoretical consideration of cuticle microstructure in CLPT, which predicts extension shear-coupling ($A_{16}, A_{26}\neq{0}$) for individual off-axis macrofiber laminae.

		To the best of our knowledge... had not previously been reported
